---
title: "Presentation01"
author: "Wesley Bortolozo"
date: "22 de outubro de 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## My new slide
Some content 

***
A slide without a title

## My title
### A top level subheading
#### A second level subheading
- Bullet One
- Bullet Two
1. Item a
2. Item b

## R Code Slide with evaluation
```{r, comment="", echo = TRUE}
head(mtcars)
```

## R Code Slide without evaluation
```{r, comment="", echo = TRUE, eval=FALSE}
head(mtcars)
```

## Plot Slide
```{r, echo=FALSE, fig.cap='My Awsome Figure', fig.align='center'}
plot(mtcars$wt, mtcars$mpg, xlab = 'Weight', ylab = 'MPG')
```


## Another New Slide
Plain text


*italicized text*


**Bold text**


`for (i %in% 1:10):`

## R Markdown
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets
- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output
```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot
```{r pressure, echo = TRUE}
plot(pressure)
```

